Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-03-27 analysis/paper/paper.Rmd
Moved wrangling and target species sets higher in paper.Rmd. Also changed some small data sets made in scripts so paper.Rmd knits without issue.

```
*Site Accessibility*
How consistently are they able to conduct surveys at each site? E.g., how often is Site 1 dropped due to cruise ships?

@@

```{r SurveyEffort, eval=TRUE, cache = FALSE, include = FALSE}
#source("../scripts/survey_duration.R", echo=FALSE)
```

```{r Fig-SurveyEffort, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap=""}
#print(plot_duration)
```

>>>>

*Site Accessibility*
How consistently are they able to conduct surveys at each site? E.g., how often is Site 1 dropped due to cruise ships?

@@

```{r SurveyEffort, eval=TRUE, cache = FALSE, include = FALSE}
source("../scripts/survey_duration.R", echo=FALSE)
```

```{r Fig-SurveyEffort, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap=""}
print(plot_duration)
```
